Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-11-17 tacl.tex
Final version

In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In this, a FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework. Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians. Note that the FS framework allows for individual morphemes to be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.

>>>>

In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' In this, an FS shows signs of being part of a mental lexicon.\footnote{Though by this definition individuals or small groups may have their own FS, here we are only interested in FS that are shared by a recognizable language community.} As noted by Wray \shortcite{Wray08},  formulaic sequence theory is compatible with other highly multiword, lexicalized approaches to language structure, in particular Pattern Grammar \cite{PG} and Construction Grammar \cite{ConG}; an important distinction, though, is that these sorts of theories often posit entirely abstract grammatical constructions/patterns/frames which do not fit well into the FS framework. Nevertheless, since many such constructions \textit{are} composed of sequences of specific words, the FS inventory of a language includes many flexible constructions (\eg \ex{ask \gap for}) along with entirely fixed combinations (\eg \ex{rhetorical question}) not typically of interest to grammarians. Note that the FS framework allows for individual morphemes to be part of a formulaic sequence, but for practical reasons we focus primarily on lemmatized words as the unit out of which FS are built.
